The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2019-09-10 tex/VHzQ.tex
Updated Appendix to remove SDSSJ0835+3227 details, included figure

There were two QSOs in the Perger catalogue which could not be immediately fixed
by looking up the original coordinates in the literature: SDSSJ0835+3227 and VA-13492.
In both cases the coordinates looked similar to SDSSJ0835+3217 and
SDSSJ1040-1155, respectively, and the stated redshifts were identical to these
quasars. In the case of SDSSJ0835+3227, we checked the SDSS $z$-band
images\footnote{https://dr15.sdss.org}, and found a bright source at
the position of SDSSJ0835+3217 and no source at the position of
SDSSJ0835+3227, see Figure~\ref{fig:check_obj}. In the case of
VA-13492, the $i$-band magnitude was equivalent to SDSS J1040-1155
($i=25.9$ mag), so we have decided that both of these objects have
been transcribed incorrectly sometime in the past. The SDSSJ1040-1155 
transcription error seems to have occurred after \cite{Douglas2007} and is in
\cite{Flesch2015}, so it probably occurred in the \cite{Flesch2015}.

@@

\begin{figure}
  %% trim=l b r t
  % \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm]{checkQsoPlots/sdssJ083525+3217.jpg}
  \includegraphics[width=8.6cm]{checkQsoPlots/sdssJ083526+3227.jpg}
  \centering
  %\vspace{-12pt} 
  \caption[]
  {{\bf Cutouts from SDSS z-band images retrieved from SDSS-SkyServer for the
  coordinates of SDSSJ083535+3217 and SDSSJ083526+3227. Both of these objects
  appear in \cite{Banados2016} and subsequently in the Perger catalogue, but
  only SDSSJ083535+3217 is matched to an SDSS source. Since SDSSJ083526+3227
  has an SDSS name, and is apparently a $z=5.89$ QSO, it should have a z-band
  detection.}}
  \label{fig:check_obj}
\end{figure}

>>>>

There was one QSO in the Perger catalogue which could not be immediately fixed
by looking up the original coordinates in the literature: VA-13492.
In this case the coordinates looked similar to SDSSJ1040-1155, and
the stated redshift was identical, $z=5.44$. Additionally, in this case,
the $i$-band magnitude was equivalent to SDSS J1040-1155
($i=25.9$ mag), so we have decided that both of these objects are the same and 
have been transcribed incorrectly sometime in the past. The SDSSJ1040-1155 
transcription error seems to have occurred after \cite{Douglas2007} and is in
\cite{Flesch2015}, so it probably occurred in \cite{Flesch2015}.

@@
